%-------------------------
% CV - Ilia Karmanov
% Compile with: tectonic Karmanov.tex
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\cventry}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\cvpub}[1]{\item\small{#1}\vspace{-2pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlist[itemize]{leftmargin=0.15in}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \textbf{Ilia Karmanov}} \\[6pt]
    \small
    Zurich, Switzerland \quad $\cdot$ \quad
    \href{mailto:ilia.uk@gmail.com}{ilia.uk@gmail.com} \quad $\cdot$ \quad
    \href{https://ilkarman.github.io}{ilkarman.github.io} \quad $\cdot$ \quad
    +41 76 803 1861
\end{center}

%----------OVERVIEW----------
\section{Overview}
\small{
Research Scientist (Senior Staff) at NVIDIA ADLR, working on vision-language models and reinforcement learning for multimodal reasoning. First-authored Eclair, used in the Nemotron-H pre-training pipeline. Previously published at NeurIPS, ICCV, and BMVC at Qualcomm AI Research, with 12 patent applications. Trained in economics at LSE (BSc, First Class; MSc) with a focus on optimal control and causal inference; transitioned into machine learning in 2016.
}

%-----------EXPERIENCE-----------
\section{Experience}
  \begin{itemize}[leftmargin=0.15in, label={}]

    \cventry
      {NVIDIA ADLR, Zurich}{Mar 2025 -- present}
      {Senior Staff Research Scientist}{}
      \begin{itemize}
        \item Started NVIDIA's first GRPO training pipeline on hybrid Mamba-Transformer architectures for visual reasoning (later completed by colleagues for Nemotron). Through systematic rollout analysis, identified that visual perception---not reasoning---was the primary bottleneck, which informed the team's approach to multimodal reasoning (MathVista, MMMU-Pro, MMLongBench)
        \item Currently working on multi-hop visual reasoning and Nemotron VL V3
      \end{itemize}

    \cventry
      {NVIDIA ADLR, Zurich}{Sep 2022 -- Feb 2025}
      {Staff Research Scientist}{}
      \begin{itemize}
        \item Created Eclair, a document understanding model designed to serve two purposes: as architecture R\&D for vision-language encoders and as a high-fidelity extraction system (LaTeX, code, equations) for LLM pre-training data. Led architecture design, training strategy, and the paper. The model shipped as Nemotron Parse and provided 50B+ text tokens to NVIDIA's LLM pre-training pipeline
        \item Identified and solved a data-conditioning failure where the model learned to rely on visual appearance rather than text prompts across heterogeneous data sources. Developed a self-correcting labelling method---masking incorrect predictions and re-feeding as valid samples---now patented
        \item Contributed architecture guidance for Eagle 2 (NeurIPS 2025) on token compression for dense OCR tasks. Mentored two interns who converted to full-time; one now leads Nemotron Parse
      \end{itemize}

    \cventry
      {Qualcomm AI Research, Amsterdam}{2021 -- 2022}
      {Staff Research Scientist}{}
      \begin{itemize}
        \item Developed hardware-efficient architectures for 4K video-to-video processing (denoising on device)
        \item Efficient Mixture-of-Experts architecture for conditional computation (BMVC 2022)
      \end{itemize}

    \cventry
      {Qualcomm AI Research, Amsterdam}{2020 -- 2021}
      {Senior Research Scientist}{}
      \begin{itemize}
        \item Created first unsupervised approach for 3D person-localisation on video and WiFi data. Published at NeurIPS 2021 (with Max Welling) and IEEE GLOBECOM 2021 (first author)
        \item Video recognition via motion-augmented self-training (ICCV 2021, with Cees Snoek)
        \item Hand-gesture classification for mmWave data (high-frequency radio), on-device and in real-time (IEEE WCNC 2021)
        \item Filed 12 patent applications across positioning, gesture recognition, and efficient architectures
      \end{itemize}

    \cventry
      {Microsoft, London}{2018 -- 2020}
      {Senior Applied Scientist}{}
      \begin{itemize}
        \item Semantic segmentation: fully and self-supervised pretraining on various data modalities (X-rays, seismographs)
        \item Object detection: supervised counting for industrial pipe inspection and store-shelf product identification
        \item Video action recognition: real-time person action recognition and localisation
        \item Synthetic data pipelines: improving generalisation through inductive biases (low-frequency/shape signals)
      \end{itemize}

    \cventry
      {Microsoft, London}{2016 -- 2018}
      {Applied Scientist}{}
      \begin{itemize}
        \item Collaborated with MSR on Z3 theorem-prover for plane-gate allocations (Dubai Airport)
        \item Created \href{https://github.com/ilkarman/DeepLearningFrameworks}{DeepLearningFrameworks}: benchmarking deep learning frameworks across single-node and multi-node on Azure. 1,700+ GitHub stars, contributions from framework creators
      \end{itemize}

    \cventry
      {Charles River Associates, London}{2014 -- 2016}
      {Senior Associate}{}
      \begin{itemize}
        \item Econometric analysis of cross-sectional, time-series, and panel data for antitrust litigation
        \item Network/graph theory for store-customer relationships; computational geometry for merger analysis
      \end{itemize}

    \cventry
      {International Growth Centre (Oxford)}{2013 -- 2014}
      {Research Economist}{}
      \begin{itemize}
        \item Research centre directed by Prof.\ Paul Collier. Contributed to research on firm capabilities, entrepreneurship, and trade
      \end{itemize}

    \cventry
      {London School of Economics}{2013 -- 2014}
      {Research Assistant to Prof.\ Frank Cowell}{}
      \begin{itemize}
        \item Simulations on measures of inequality (Matlab, Stata). Causal inference (diff-in-diff) on European identity and redistribution preferences, resulting in published paper (Costa-Font \& Cowell, 2015)
      \end{itemize}

  \end{itemize}

%-----------PUBLICATIONS-----------
\section{Publications}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \cvpub{\textbf{I Karmanov}, A Deshmukh, L Voegtle, P Fischer, K Chumachenko, T Roman, J Seppanen, J Parmar, J Jennings, A Tao, K Sapra. Eclair: Extracting Content and Layout with Integrated Reading Order for Documents. arXiv 2025}
    \cvpub{K Chumachenko, A Deshmukh, J Seppanen, \textbf{I Karmanov}, C Chen, L Voegtle, P Fischer, et al. Nemotron Parse 1.1. arXiv 2025}
    \cvpub{140+ authors incl.\ \textbf{I Karmanov}. NVIDIA Nemotron Nano V2 VL. arXiv 2025}
    \cvpub{199 authors incl.\ \textbf{I Karmanov}. Nemotron-H: A Family of Accurate and Efficient Hybrid Mamba-Transformer Models. arXiv 2025}
    \cvpub{Z Li, G Chen, S Liu, ... \textbf{I Karmanov}, L Voegtle, P Fischer, ... Z Yu. Eagle 2: Building Post-Training Data Strategies from Scratch for Frontier Vision-Language Models. NeurIPS 2025}
    \cvpub{A Royer, \textbf{I Karmanov}, A Skliar, B Ehteshami Bejnordi, T Blankevoort. Revisiting Single-gated Mixtures of Experts. BMVC 2022}
    \cvpub{FG Zanjani, \textbf{I Karmanov}, H Ackermann, D Dijkman, S Merlin, M Welling, F Porikli. Modality-Agnostic Topology Aware Localization. NeurIPS 2021}
    \cvpub{\textbf{I Karmanov}, FG Zanjani, S Merlin, I Kadampot, D Dijkman. WiCluster: Passive Indoor 2D/3D Positioning using WiFi without Precise Labels. IEEE GLOBECOM 2021}
    \cvpub{K Gavrilyuk, M Jain, \textbf{I Karmanov}, CGM Snoek. Motion-Augmented Self-Training for Video Recognition at Smaller Scale. ICCV 2021}
    \cvpub{Y Ren, J Lu, A Beletchi, Y Huang, \textbf{I Karmanov}, et al. Hand Gesture Recognition using 802.11ad mmWave. IEEE WCNC 2021}
    \cvpub{FG Zanjani, H Ackermann, D Dijkman, \textbf{I Karmanov}, et al. Deep Learning Frameworks for Weakly-Supervised Indoor Localization. NeurIPS 2021 (Competition \& Demos)}
    \cvpub{J Costa-Font, F Cowell (with research contributions from \textbf{I Karmanov}). European Identity and Redistributive Preferences. CESifo Working Paper, 2015}
  \end{itemize}

\section{Book}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \cvpub{M Salvaris, D Dean, WH Tok, \textbf{I Karmanov}. Deep Learning with Azure: Building and Deploying Artificial Intelligence Solutions on the Microsoft AI Platform. Apress, 2018}
  \end{itemize}

\section{Patents}
\small{
10 granted/pending US patents across WiFi positioning, gesture recognition, and efficient architectures, including:
}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \cvpub{Passive positioning with radio frequency sensing labels (US 11,755,886)}
    \cvpub{Passive positioning with radio frequency sensing (US 11,575,452)}
    \cvpub{Self-supervised passive positioning using wireless data (US 11,871,299; US 12,022,358)}
    \cvpub{Multi-object positioning using mixture density networks (US 11,696,093)}
    \cvpub{MoE and model ensembling (US App. 18/154,429)}
    \cvpub{Localization through manifold learning and optimal transport (US App. 17/804,842)}
    \cvpub{+ 3 additional patent applications}
  \end{itemize}

%-----------TALKS-----------
\section{Select Talks}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \cvpub{\textbf{I Karmanov}, FG Zanjani, S Merlin, I Kadampot, D Dijkman. Demonstrating Accurate RF Sensing with Qualcomm Wi-Fi Technology. MWC 2021}
    \cvpub{L Zhang, T Wu, X Xie, A Argyriou, \textbf{I Karmanov}, K Lian. Building Production-Ready Recommendation System at Scale. KDD 2019}
    \cvpub{M Gonzalez-Fierro, D Dean, M Salvaris, \textbf{I Karmanov}. Microsoft AI Transformation. IROS 2018}
    \cvpub{\textbf{I Karmanov}, M Salvaris, M Gonzalez-Fierro. Distributed Training of Deep Neural Networks. ODSC 2018 / Strata 2018}
    \cvpub{\textbf{I Karmanov}, F Boylu-Uz. Linear Programming on Azure for Plane-Gate Optimisation. MLADS 2018}
  \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \cventry
      {London School of Economics}{2012 -- 2013}
      {MSc Economics, with Merit}{}
      \begin{itemize}
        \item Thesis: Optimal Control Analysis for Tax Avoidance. Modelling a firm's optimisation problem in an infinite horizon setting, introducing reputation as an accumulated asset, solved with Hamiltonian in an optimal-control setting. Advisor: Prof.\ Frank Cowell
      \end{itemize}
    \cventry
      {London School of Economics}{2009 -- 2012}
      {BSc Economics, First Class Honours}{}
      \begin{itemize}
        \item Highest final-year average in cohort
      \end{itemize}
  \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
  \begin{itemize}[leftmargin=0.15in]
    \item\small{CRA Innovation Grant (\$20k) for developing new geospatial analytical tools (2015)}
    \item\small{Youngest person to pass a Computer Science A-Level (BBC News, 2002)}
    \item\small{Youngest person to pass an Economics A-Level (BBC News, 2005)}
  \end{itemize}

\end{document}
